Machine Learning Autoencoder Applied to Communication Channels

### 2019-08-26 Rapport/Presentation PIR/Presentation/Presentation.tex
Inicio TG

\author{E.~Dadalto Camara Gomes\inst{1}}
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.

\institute[] % (optional, but mostly needed)
{
  \inst{1}%
   ISAE-SUPAERO\\
   Université de Toulouse\\
    31055, Toulouse, France\\
Email: eduardo.dadalto-camara-gomes@student.isae-supaero.fr
%  \and
 % \inst{2}%
 % Department of Electronics, Optronics, and Signal processing\\
 % ISAE-SUPAERO\\
 % 31055, Toulouse, France\\
 % Email: meryem.benammar@isae-supaero.fr
 }
% - Use the \inst command only if there are several affiliations.
% - Keep it simple, no one is interested in your street address.

@@

\begin{outline}
 \1 Low latency and high bandwidth wireless communication are key to critical systems.
   \2 i.g. airplanes, satellites, cellular communication and 5G operations.
\pause
 \1 As opposite to structured algorithms, machine learning (ML) algorithms do not require rigidly designed models and can take non-linearities effortlessly into account.
\pause
 \1  ML based communication systems could be a better representation of realistic systems and could optimize information transmission of different blocklengths.
   \2 It translates to lower decoding latency, resulting ultimately in gain of bandwidth over standard methods.

@@

\begin{outline}
\1 Could ML based decoders and autoencoders for a BSC perform similarly to the MAP decoder in real applications and have lower communication delay?
\pause
\1 This work aims to contribute to set up a higher standard in terms of performance in bit-error correction and demonstrate that ML based models can reduce delay for digital communication applications. 
\end{outline}

@@

\begin{frame}{DNN Autoencoder Design}{}
	\begin{figure}[!ht]
  \centering
    \includegraphics[width=0.6\textwidth]{images/DNN_autoencoder}
    \caption{Representation of a DNN autoencoder composed of dense layers. Each block represents a DNN which together learn the channel encoding and decoding in an end-to-end manner. They also operate together in bit error correction.}\label{fig:DDNNAutoencoder}
\end{figure}
\end{frame}

\begin{frame}{Array Autoencoder DNN Architecture and Implementation}{This design yielded best error correction results out of 80 models tried}
    \begin{table}
\caption{DNN array autoencoder architecture and training parameters.} 
\begin{center}
  \begin{tabular}{ l  |  l }
    \thickhline
    \multirow{3}{*}{Encoder} & Dense: 512, activation: ReLU, BN\footnotemark, input size: 8 \\
 & Dense: 256, activation: ReLU, BN \\
 & Dense: 16, activation: Sigmoid  \\ \hline
    \multirow{2}{*}{Channel} & Lambda: $Round(\textbf{x})$, input size: $16$ \\
 & Lambda: $\textbf{x}\oplus \text{noise}$\\ \hline
 \multirow{2}{*}{Decoder} & Dense: 128, BN, input size: 16 \\
 & Dense: 64, activation: ReLU, BN  \\
 & Dense: 8, activation: Sigmoid  \\ \hline
    \multicolumn{2}{l}{\textbf{Total parameters: }154072}\\
    \thickhline
  \end{tabular}
    \label{tab:arrayautoencoder}
\end{center}
\end{table}

@@

\section*{Acknowledgment}
\begin{frame}{Acknowledgment}
  I would like to thank ...
  \begin{itemize}
   \item{The guidance and advice from my supervisor Mme. Meryem Benammar, Ph.D;}
  \item{ My colleague Rémy Zawislak who worked in the same theme and collaborated indirectly to the research;}
   \item{Mme. Marjorie Grzeskowiak Lucas, Ph.D, who through the Institut Supérieur de l'Aéronautique et de l'Espace (ISAE-SUPAERO) enabled the confection of the project; and }
   \item{The evaluators, the LACS member and the audience.}
  \end{itemize}
\end{frame}

>>>>

\author{E.~Dadalto Camara Gomes\inst{1} \and M.~Benammar\inst{2}}
% - Give the names in the same order as the appear in the paper.
% - Use the \inst{?} command only if the authors have different
%   affiliation.

\institute[] % (optional, but mostly needed)
{
  \inst{1}%
   ISAE-SUPAERO\\
   Université de Toulouse\\
    31055, Toulouse, France\\
Email: eduardo.dadalto-camara-gomes@student.isae-supaero.fr
  \and
  \inst{2}%
  Department of Electronics, Optronics, and Signal processing\\
  ISAE-SUPAERO\\
  31055, Toulouse, France\\
  Email: meryem.benammar@isae-supaero.fr
 }
% - Use the \inst command only if there are several affiliations.
% - Keep it simple, no one is interested in your street address.

@@

\begin{outline}
 \1 Low latency and high bandwidth wireless communication are key to critical systems.
   \2 i.g. airplanes, satellites, cellular communication and 5G operations.
\pause
 \1 As opposite to structured algorithms, machine learning (ML) algorithms do not require rigidly designed models and can take non-linearities effortlessly into account.
\pause
 \1  ML based communication systems could be a better representation of realistic systems and could optimize information transmission of different blocklengths.

@@

\begin{block}{Hypothesis}
Could ML based decoders and autoencoders for a BSC perform similarly to the MAP decoder in real applications and have lower communication delay?
\end{block}
\pause
\begin{block}{Objective}
This work aims to contribute to set up a higher standard in terms of performance in bit-error correction and demonstrate that ML based models can reduce delay for digital communication applications. 
\end{block}
\end{frame}

@@

%%\begin{frame}{DNN Autoencoder Design}{}
%	\begin{figure}[!ht]
%  \centering
%    \includegraphics[width=0.6\textwidth]{images/DNN_autoencoder}
%%    \caption{Representation of a DNN autoencoder composed of dense layers. Each block represents a DNN which together learn the channel encoding and decoding in an end-to-end manner. They also operate together in bit error correction.}\label{fig:DDNNAutoencoder}
%\end{figure}
%\end{frame}

\begin{frame}{Array Autoencoder DNN Architecture and Implementation}{This design yielded best error correction results out of 80 models tried}
    \begin{table}
\caption{DNN array autoencoder architecture and training parameters.} 
\begin{center}
  \begin{tabular}{ l  |  l }
    \thickhline
    \multirow{3}{*}{Encoder} & Dense: 512, activation: ReLU, BN\footnotemark, input size: 8 \\
 & Dense: 256, activation: ReLU, BN \\
 & Dense: 16, activation: Sigmoid  \\ \hline
    \multirow{2}{*}{Channel} & Lambda: $Round(\textbf{x})$, input size: $16$ \\
 & Lambda: $\textbf{x}\oplus \text{noise}$\\ \hline
 \multirow{2}{*}{Decoder} & Dense: 128, activation: ReLU, BN, input size: 16 \\
 & Dense: 64, activation: ReLU, BN  \\
 & Dense: 8, activation: Sigmoid  \\ \hline
    \multicolumn{2}{l}{\textbf{Total parameters: }154072}\\
    \thickhline
  \end{tabular}
    \label{tab:arrayautoencoder}
\end{center}
\end{table}

@@

%%\section*{Acknowledgment}
%\begin{frame}{Acknowledgment}
%  I would like to thank ...
%  \begin{itemize}
%   \item{The guidance and advice from my supervisor Mme. Meryem Benammar, Ph.D;}
%  \item{ My colleague Rémy Zawislak who worked in the same theme and collaborated indirectly to the research;}
%   \item{Mme. Marjorie Grzeskowiak Lucas, Ph.D, who through the Institut Supérieur de l'Aéronautique et de l'Espace (ISAE-SUPAERO) enabled the confection of the project; and }
 %  \item{The evaluators, the LACS member and the audience.}
 % \end{itemize}
%\end{frame}
